Thank You, Next

### 2022-11-17 Manuscript/manuscript_draft.tex
10/17/22 commit

\section*{Methods}
\subsection*{Study System}

To determine how interactions with multiple partners impacts the cacti over time, we have monitored a population of Cholla cacti annually since 2004. 
This study was conducted in the Los Pinos mountains, a small mountain chain located on the Sevilleta National Wildlife Refuge, a Long-term Ecological Research (LTER) site in central New Mexico. 
The tree cholla cacti are common in high Chihuahuan desert habitats, with their native range spanning the southwestern USA *** Benson 1982***. 
These arborescent cacti produce new cylindrical segments every year which develop either into fruits which produce seeds or into vegetative segments with large spine which increase the size of the cactus %***Miller, Tenhumberg \& Louda 2008***. 
In central New Mexico, vegetative growth occurs from May -- August.

Cholla cacti secrete extra-floral nectar (EFN) from glands on young vegetative segments and reproductive segments. 
\tom{This extra-floral nectar varies in chemical makeup across the lifespan of the cactus *** Miller ??***. }{This is pretty vague, so if you are going to say this you should add more detail.}
At the Sevilleta, the cacti are visited by \tom{multiple species}{I think it would be better to say primarily two species plus other rare species, and giving the frequencies} of ground-nesting ants, \textit{Crematogaster opuntiae}, \textit{Liometopum apiculatum}, and \tom{many other species}{which ones?} which occur at \tom{small}{low} frequencies. 
These ants are attracted to the EFN and in return fight off the \tom{seed predators}{which ones?} \tom{which also visit the cacti}{An example of words that make sentences clunky without adding any information}. 
These ants never co-occur on the same plant, \tom{instead competing for plant services}{This is a hypothesis, not something that has been demonstrated.}. 
\tom{Over the lifetime of the cacti each plant interacts with multiple partners as they tend to switch out season to season.}{I would guess that most plants do not have much switching. I think you also need to talk about vacancy and the start of EFN production at larger reproductive sizes, more detail on transitions in ant state between vs within years. All of this should be in a separate subsection about natural history.}

\tom{There}{This paragraph should also be in a natural history subsection and obviously needs more detail. See my earlier papers and references therein and let me know if you have specific questions.} are a variety of insect herbivores and seed predators which attack the cacti, focusing either on the vegetative segments and the reproductive segments. 
There are a number of insects which occur commonly on these cacti at the Sevilleta. 
These include the weevil, the NP, and the *** (I think there is a moth as well?). 
The \tom{weevil}{what species?} feeds on ***. 
The NP feeds on ***. 
Finally, the moth?? feeds on ***. 
All of these predators can have significant impacts on the fitness of both individual cacti and the population. *** Miller 2009***.

\tom{The}{This should be a subsection for data collection, with significantly more information than what you have here so that the methods could be reproduced.} data collected on these cacti are from an \tom{18-year}{Which years?} data-set. 
There are 8 30 $\times$ 30 meter plots from which this data is taken. 
Each plot is \tom{surveyed}{what does this mean?}, and each plant within each plot is tagged and \tom{logged}{what does this mean} each year. 
For every plant we take data on their survival, \tom{size}{how is size measured?}, \tom{ant state}{what is this?}, \tom{herbivore presence}{this makes it sounds like presence/absence which is not what we record}, \tom{flowering data}{what does this mean?}, and \tom{seed data}{what does this mean?}. 
\tom{This allows us to track the progression of individual plants across many years.}{No new information here.} 
The length of this data-set

\subsection*{Statistical Modeling}
To understand the impacts of multiple species interactions on the cacti populations, we constructed \tom{bayesian demographic models of many vital rates}{What are bayesian demographic models? WHat are the many vital rates?}. 
With these models, we were able to ask (i) Do the impacts of ant presence on \tom{cacti fitness}{these models are not measuring fitness} differ across ant species? (ii) What are the probabilities of an individual cactus interacting with each ant species?.\tom{}{I think it's good that you have these as separate questions but I think each one needs a lot more context and detail.}

The vital rates of the cacti considered in this model include survival rate, growth rate, reproductive state, floral abortion rate, \tom{seed production, and germination}{You have not described where these data come from.}. 
\tom{We fit generalized linear mixed effects models in a heirarchical Bayesian framework to quantify each of the vital rates.}{Not a reproducible description of the methods. e.g., what distributions were used, what were the fixed and random effects, which models included ant effects, what were the priors, how many chain and iterations, and were convergence and fit assessed, etc?} 
\tom{Each model takes the data from year \textit{t} and estimates the values in year \textit{t+1}.}{This is true only for growth and survival.} 
This allows us to predict a vital rate for any plant with a given set of characteristics, \tom{such as size and ant state}{Not such as, it is really just these two things.}. 
\vspace{1cm}

@@

The statistical models described above parameterize the Integral Projection Model (IPM) that we used to estimate population growth under various partner conditions.  
This model was used to estimate the growth rate of the cactus population, effectively a quantitative measure of the fitness of the population. 
The fitness was estimated under the \tom{range of all different conditions, no ants present, one ant species present, two ant species present, all ant species present.
These allow us to compare the fitness of the cacti under no mutualistic interactions, pairwise mutualisms, and various multi-species mutualisms to show which case results in the highest fitness for the cacti.}{This needs a more thorough explanation, but I would also do this later after the model has been introduced and explained.}

@@

The final equation gives the \tom{size}{not just population size but also composition in terms of size and ant state - this needs to be explained better} of the \textit{C. imbracata} population $n$ in year $t+1$ based on the vital rates and size $n$ of the population in year $t$.
The first term gives the recruitment from 1 and 2-year seedbanks to size $y$.
$\eta(y)$ gives the seedling size distribution, which is assumed to be normally distributed, and $\omega$ gives the proportion of seedlings which survive from germination (late summer) to the census (May). 
The second term gives the changes in the population of the cacti which are not recruits. 
The functions $S$ and $G$ give the probabilities of surviving from year $t$ to $t+1$ and growing to size $y$ from year $t$ to year $t+1$, respectively. 
Each depends on the size $x$ in year $t$ and the ant state $j$ in year $t+1$. 
Finally, $\tau_{ij}$ is the probability of a cactus which is size $x$ with ant partner $i$ in year $t$ being tended by ant partner $j$ in year $t+1$.

 \subsection*{Model analysis}

\textbf{TOM STOPPED EDITING HERE}

\section*{Results}
\subsection*{Vital Rates}

We used field data on cholla cacti to evaluate the differing impacts that the ant mutualism has on the fitness of the cacti. The fitness can be broken down into a number of vital rate components, including survival, growth, probability of flowering, number of fruits and seeds produced, etc. called vital rates. We found that many of these vital rates differ in the presence of different ant species.

\begin{figure}[!ht]
	\centering
	\includegraphics[width = 0.85\linewidth]{Figures/surv_panels_cropped.png}
	\caption{Probability of cactus survival from year t to year t+1 when tended by (a) \textit{Crem.} (Purple), (b) \textit{Liom.} (Teal), (c) ants in the other category (Pink), or (d) no ants (Yellow). Panels (a-d) show the best-fit line estimating the survival probabilities of cacti, with a grey area representing the uncertainty, and circles representing the actual data (scaled to represent number of observations). (e) shows the best-fit probabilities of survival of different-sized cacti with all ant partners.}
	\label{fig:surv}
\end{figure}

	The first vital rate we analyzed was the survival of the cacti. As you can see in Figure \ref{fig:surv}, the survival rate of cacti vary significantly across their lifetimes as they grow. Young (small) cacti have relatively low survival rates, near $30\%$ while the older mature cacti have much higher survival rates, near $100\%$. This means cacti are at their most vulnerable to death when they are young. The survival rates differ with more than just the size of the cacti, the ant species present on the cactus is also important.

There are no very small cacti tended by ant partners because they do not produce EFN. This is reflected in Figure \ref{fig:surv} where only the vacant data (yellow) in panel (d) extends to the smallest sizes. Once cacti reach a size large enough to attract ant partners with EFN, the cacti which are partnered with \textit{Crem.} have the highest survival rates compared to all other cacti. When the cacti reach their larger sizes, the partnered plants all reach a nearly $100\%$ survival rate while plants with no partners have a slightly lower survival rate for all large cacti. This result indicates that \textit{Crem.} tended plants may have an advantage, when they are relatively small, over other cacti.

The next vital rate we analyzed was the viability rate of the cacti, the proportion of fruits produced which are viable for reproduction. It is clear from Figure \ref{fig:viab} that the cacti tended by \textit{Liom.} ants experience significantly higher proportions of viable fruits. This result aligns with much of the literature which shows that \textit{Liom.} are more aggressive against herbivores and seed predators, therefore are very high quality defenders. This high-quality defense is imperative for high viability rates on reproducing cacti which are likely to attract many antagonists due to the quality of their EFN.

\begin{figure}[!ht]
	\centering
	\includegraphics{Figures/viab_hist.png}
	\caption{Proportion of viable fruits produced by a cactus in year t+1 when tended in year t by (a) \textit{Crem.} (Purple), (b) \textit{Liom.} (Teal), (c) ants in the other category (Pink), or (d) no ants (Yellow). Each panel (a-d) shows a histogram of the actual data overlayed with a density distribution of the predicted viability rate of the cacti. Panel (e) shows the predicted distributions of viability rates separated by ant species.}
	\label{fig:viab}
\end{figure}

A third vital rate considered in this paper is the growth rate. Cacti who are attacked by herbivores are likely to lose sections of their growth, leading to a lower, or even negative, growth rate. In Figure \ref{fig:grow} you can clearly see that untended plants are the only cacti which experience a negative growth rate at any size. This again aligns with expectations that tended cacti are being defended from herbivores and are therefore unlikely to lose enough vegetation to result in a negative growth rate.

\begin{figure}[!ht]
	\centering
	\includegraphics{Figures/grow_panel.png}
	\caption{The size of a cactus in year t+1 given a previous size in year t and being tended by (a) \textit{Crem.} (Purple), (b) \textit{Liom.} (Teal), (c) ants in the other category (Pink), or (d) no ants (Yellow). Each panel (a-d) shows a best-fit prediction of the future size based on the previous size, the uncertainty in grey surrounding the best-fit, and the actual data in (circles scaled to represent the number of observations). Panel (e) shows all best-fit lines together in the same colors as above and a line (grey, dashed) above which plants are growing (have a positive growth rate) and below which plants have a negative growth rate.}
	\label{fig:grow}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics{Figures/grow_dist_panel2.png}
	\caption{The size of a cactus in year t+1 given a previous size in year t and being tended by (a) \textit{Crem.} (Purple), (b) \textit{Liom.} (Teal), (c) ants in the other category (Pink), or (d) no ants (Yellow). Each panel (a-d) shows a distribution of the predicted future size based on the previous sizeand a histogram of the actual data. Panel (e) shows all predicted distributions together in the same colors as above.}
	\label{fig:grow2}
\end{figure}

	\subsection*{Ant Transition Rates}

In addition to the vital rates of the cacti, we also analyzed the transition rates from one ant partner to another across years.

\begin{table}[]
	\centering
	\begin{tabular}{|p{0.25 \linewidth}   |p{0.25 \linewidth}|p{0.25 \linewidth}|}
		\hline
		\textbf{Ant States Possible} & \textbf{Growth Rate ($\frac{n_{t+1}}{n_t}$)} & \textbf{Population $\lambda$}\\
		\hline
		No ants & &\\
		\hline
		\textit{Liom.} & & \\
		\hline
		\textit{Crem.}  & & \\
		\hline
		Other & & \\
		\hline
		\textit{Liom.} \& \textit{Crem.} & & \\
		\hline
		\textit{Liom.} \& Other & & \\
		\hline 
		\textit{Crem.} \& Other & & \\
		\hline
		\textit{Liom.}, \textit{Crem.} \& Other & & \\
		\hline
	\end{tabular}
	\caption{Caption}
	\label{tab:table_sims}
\end{table}
%	\begin{multicols}{2}

\section*{Discussion}

There is a constant tension within life cycles between energy and resource allocation. Individuals often have the ability to either put significant resources towards one process or split their resources between multiple. Full energy allocation to one process generally means better results, but splitting resources is a form of bet hedging ***. The cacti studied here experience a certain tension between their many vital rates, particularly growth and reproduction because each year they produce new floral buds and new vegetative growth. Small plants rarely put out flowers and instead focus on growth, but larger plants must choose each year. The analyses of the individual vital rates indicate that different ant species may protect different processes better than others. In particular \textit{Crem.} may offer advantages to smaller plants by protecting their new vegetation well. This is seen in the higher survival rates and growth rates of small and medium cacti with \textit{Crem.} tenders in Figure \ref{fig:grow} and Figure \ref{fig:surv}. \textit{Liom.} ants alternatively may protect reproductive focus more than other partners. The \textit{Crem.} tended plants however, have lower viability rates than any other ant tended plants, indicating they do not protect flowers well from herbivores(Figure \ref{fig:viab}). This is seen in Figure \ref{fig:viab} where it is shown that plants tended by \textit{Liom.} have the highest viability rates of their flowers, resulting in higher pollination rates. Larger plants are also less likely to lose branches when they are tended by \textit{Liom.} (Figure \ref{fig:grow}), keeping them healthy and more able to generate new plants. Each of these ants individually offer both benefits and drawbacks but considered together may indicate complementarity across ontogeny.

>>>>

\section*{Methods}
\subsection*{Study System}
\subsection*{Natural History}
To determine how interactions with multiple partners impacts the cacti over time, we have monitored a population of tree cholla annually since 2004. 
This study was conducted in the Los Pinos mountains, a small mountain chain located on the Sevilleta National Wildlife Refuge, a Long-term Ecological Research (LTER) site in central New Mexico (34*20’5.3’’N, 106*37’53.2’’W).
This is an area characterized by steep, rocky slopes, perennial vegetation like cacti and junipers. 
The tree cholla cacti are common in high Chihuahuan desert habitats, with their native range spanning the southwestern USA\cite{Benson1982}. 
These arborescent cacti produce cylindrical segments with large spines. 
In the growing season, May to August in New Mexico, the plants initiate new vegetative segments and flower buds at the ends of existing segments. 
While most plants produce new segments every season, only those which are mature enough produce flower buds. 
Tree cholla generally reach at least 9 years of age before beginning to reproduce *** I found this being cited as unpublished data in Ohm Miller 2014 ***. 
Like other EFN-bearing cacti, tree cholla cacti secrete nectar from specialized glands on young vegetative or reproductive structures\cite{Ness2006,Oliveira1999}.

This EFN is harvested by various ant species in return for defense. 
At the Sevilleta, the cacti are visited primarily by two species of ground-nesting ants from the formicoid clade, \textit{Crematogaster opuntiae (Crem.) } and \textit{Liometopum apiculatum (Liom.), } as well as other rarer species, including \textit{Forelius pruinosus (For.) } and \textit{Camponotus spp. (Camp.)}.

\textit{Liom.} ants were the most frequent visitors, present a  between 25\% - 60\% of cacti annually, \textit{Crem.} were present at between 0\% - 20\% of cacti, and \textit{For.} were present at between 0\% - 5\% of cacti in any given year \ref{Fig:Ant_freq}. 
It is important to note that not all cacti are visited every season, they can remain vacant, in fact up to 80\% of cacti are vacant in any given year.

These ants rarely co-occur on a plant, probably due to interspecific competition\cite{Miller2007}, rather each cactus is visited by a single ant species for the duration of a season, and the visitor can change from one season to the next. 
Across the entire lifespan cacti may interact with multiple species of partners. 
At the beginning of the growing season, when EFN production begins, the ground-nesting ants will begin visiting tree cholla.
They will visit the cacti every day during the season from early morning *** to sunset *** abandoning the cacti at night for their nests. 
In late August, the tree cholla will stop producing EFN and the ants will stop visiting until the next growing season. 
The process by which ants are sorted out onto different cacti is somewhat of a mystery, but we know several facts which likely influence the process. 
Smaller cacti are less likely to be visited because they produce very little EFN, so larger cacti are generally more desirable\cite{Miller2014}. 
Similarly, many factors go into how many vegetative segments and floral buds are produced in a particular growing season, so the more productive cacti are also more desirable. 
Some of the ant species are considered more aggressive, specifically \textit{Liom.}\cite{Miller2007}, which may be advantageous in going after more desirable cacti. 
Some ants are also more likely to retain the same tree cholla partners year after year, meaning they reduce the partner turnover experienced by individual cacti. 
These factors mean that by some hierarchy at the beginning of the season the ants claim a subset of the existing cacti and visit them regularly throughout the season, and that from season to season the same ant species may visit the same cacti, but it is not guaranteed. 
\ali{Note.}{I am not sure how much of this I should include here, since some of the turnover info is results from this paper?}
These ants defend the tree cholla from various seed predators and herbivores in exchange for the EFN.

There are a variety of insect herbivores and seed predators which attack the cacti, focusing either on the vegetative segments and the reproductive segments throughout the entire range of the tree cholla\cite{Mann1969}. 
More locally, at the Sevilleta, there are several insects which occur commonly on these cacti.
These include an unidentified weevil, a cactus bug, and a seed predator. 
The unidentified weevil of the genus \textit{Gerstaekeria} which feed on vegetative and reproductive structures and implant their larvae within the plant for the winter. 
The cactus bug, \textit{Narnia pallidicornis}, (Hemiptera: Coreidae) feed on all cactus parts with a preference for the reproductive structures \cite{Miller2006}.
The seed predator, \textit{Cahela ponderosella}, (Lepidoptera: Pyralidae) attack developing fruits pre-dispersal and oviposit in open flowers mid-growing season where larvae burrow into the ripening ovary. 
These predators can have significant negative impacts on the fitness of individual cacti and depress population growth\cite{Miller 2009}.

	\subsection*{Data}

	The data collected on these cacti are from a long-term dataset spanning 2004 to 2022 taken from our eight 30 $\times$ 30 meter plots at the Sevilleta LTER. 
	The data initially included 134 naturally occurring plants across 4 spatial blocks censused annually from 2004 to 2008.
	Six of the 30 $\times$ 30 meter plots were created with naturally occurring plants, censused from 2009 to 2014. 
	The final two plots were added to this census from 2011 onwards. 
	The distribution of these eight plots are shown in figure \ref{fig:map}.
		Annually, in May we surveyed these plots, taking many types of demographic and partner data. 
		For each plant, we recorded the height (cm), maximum crown width, and perpendicular crown width, which are used to calculate plant volume (cm3) based on the volume of a cone with the mean of maximum crown width and perpendicular crown width as the diameter. 
		We recorded plant survival from the last survey to the current survey as a binary data point, 0 (died) or 1 (survived). 
		We recorded the total number of flower buds, including how many were aborted and how many were not, which we used to calculate the viability rates of the cacti. 
		We recorded all ant species present, usually just one, and the number of ants we could count in 30 seconds. 
		We also recorded the species of herbivore or seed predator, the number present on the plant, and if there is any clear, new evidence of herbivory on the tree cholla segments.

		In addition to this primary dataset, I used several other datasets throughout the analysis in this paper.  Look at how Tom has described these. Cite these other papers which this data comes from. 
		The second dataset was *** germination rates.
		The third dataset was *** pre-census survival.
		The fourth dataset was *** $JO_fruit_data_final_dropplant0.csv$.

@@

		The statistical models described above parameterize the Integral Projection Model (IPM) that we used to estimate population growth under various partner conditions.  
		IPMs are used to estimate fitness of a population across a continuous variable, rather than using a stage- or size-specific variable to categorize the population. 
		This IPM was used to estimate the growth rate of the tree cholla population, effectively a quantitative measure of the fitness of the population.

@@

		The final equation gives the stochastic population composition in terms of size and ant state of the \textit{C. imbracata} population $n$ in year $t+1$ based on the vital rates and size $n$ of the population in year $t$.
		The first term gives the recruitment from 1 and 2-year seedbanks to size $y$.
		$\eta(y)$ gives the seedling size distribution, which is assumed to be normally distributed, and $\omega$ gives the proportion of seedlings which survive from germination (late summer) to the census (May). 
		The second term gives the changes in the population of the cacti which are not recruits. 
		The functions $S$ and $G$ give the probabilities of surviving from year $t$ to $t+1$ and growing to size $y$ from year $t$ to year $t+1$, respectively. 
		Each depends on the size $x$ in year $t$ and the ant state $j$ in year $t+1$. 
		Finally, $\tau_{ij}$ is the probability of a cactus which is size $x$ with ant partner $i$ in year $t$ being tended by ant partner $j$ in year $t+1$.

		Because many of the vital rates were ant-specific, we were able to consider the composition of the population with the presence of any single ant species, or any combination of ant species (with vacancy always included).
		These options include: complete vacancy; \textit{Liom.} and vacancy; \textit{Crem.} and vacancy; other and vacancy; \textit{Liom.}, \textit{Crem.}, and vacancy, \textit{Liom.}, other, and vacancy; \textit{Crem.}, other, and vacancy; and all ant partners and vacancy.
		We used this option to calculate the distribution of stochastic population fitness for each combination of ant partners to determine if there is benefit from partner diversity and if there is an optimal combination of partners for this system. 
		We then used these fitnesses and the yearly break-downs of the model to determine if there was evidence of any biodiversity ecosystem function mechanisms to explain any partner diversity benefits.

		\subsection*{Statistical Modeling}
		At the start of this section say for all models unless otherwise noted we used vague priors. 
		Also need to introduce the names of these functions ex: survival = s(x)
		With the primary dataset above we fit a series of generalized linear mixed models (GLMMs) in a hierarchical Bayesian framework, meaning the output is a distribution of the interaction between various factors on the highlighted variable rather than a maximum likelihood estimate with both fixed and random effects, which predicts the probability of a given process based on the size of the cacti, the presence of different ant partners, the year, and the plot.
		Unless otherwise mentioned, all models used vague priors. 
		The growth model ($G_j(y,x)$) estimated the growth rate of cacti, with fixed effects for the size and ant partner and random effects for plot and year, using a Normal distribution, with standard deviation dependent on the size of the cactus also with a Normal distribution. 
		The survival model ($S_j(x)$) estimated the probability of survival, with fixed effects for the size of the cactus and ant partner and random effects for plot and year, using a Bernoulli distribution. 
		The reproduction model ($P(x)$) estimated the probability of reproducing each year, with fixed effects for the size of the cactus and random effects for plot and year, using a Bernoulli distribution. 
		The total flowers model ($F(x)$) estimated the total flowers produced by a plant, with fixed effects for its size and random effects for plot and year, using a Truncated Negative Binomial distribution. 
		The viability model ($A_i(x)$) estimated the proportion of flowers produced by a plant which are viable (not aborted), with fixed effects for the size of the cactus and the presence of ant partners and random effects for plot and year, using a Binomial distribution.
		The ant transition rates model ($\tau_{i,j}(x)$) estimates the probability of a cactus being visited by an ant partner, with fixed effects for the size of the cactus and the previous ant partner and random effects for plot and year, using a Multinomial distribution.  
		The recruit size model ($n_j(x)$) estimates the size distribution of all recruits from a year, with no fixed or random effects, using a Normal distribution. 
		With the second dataset above, we fit a two Bayesian generalized linear models for the 
		probability of germinating from a seed in the first year ($\gamma_1$) or the second year ($1 - \gamma_1$) using a Binomial distribution.
		With the third dataset above, we fit a Bayesian generalized linear model for the probability of a seedling, which has sprouted each year, surviving to May ($\delta$) when we visit (accounting for missed mortality events), with fixed effects for the previous size and transect random effects, using a Bernoulli distribution. 
		With the fourth dataset above, we fit a Bayesian generalized linear model for the number of seeds produced by every flower on a cactus ($\kappa$) based on the ant partner, using a Negative Binomial distribution.

		These Bayesian GLMMs were run with STAN through version 4.0.2  of R using 1000 iterations, 150 warmups, 3 chains, and 1 thins. 
		To assess the convergence of our models we checked the trace of each mcmc chain (the convergence graphs are shown in the supplemental documents in Figures ***).
		To assess the fit we simulated data from the models and compared this to the real data (the fit plots are shown in the supplemental documents in Figures ***).

		With these models, we investigated the impacts of different ant species on the processes of vital rates and the probabilities of individual cacti interacting with each ant species.
		To address our first goal, we compared the effects of ant partners on the growth rate, survival rate, and the viability of flowers across sizes. 
		We also broke these effects down by every year of data to see if the impacts of ant partners varied across years. 
		To address the second goal, we compared the probability of being visited by a given ant based on each possible previous partner to note any patterns of ant tending. 
		We also broke these interactions down by every year of data to see if the patterns changed across years.

		\vspace{1cm}

		\section*{Results}
		I’m honestly not sure what all should be included here. I feel like I need a lot more info about the specifics???

		\subsection*{Vital Rates}
		The results of the Bayesian growth model show the probability of a cactus being a specific size given the size in the previous year and the ant partner in Figure \ref{fig:grow}.
		Our analyses showed that plants of a specific size were more likely to grow larger by the next year if tended by certain ant partners. 
		Plants tended by \textit{Crem.} ants had higher growth rates than tree cholla tended by any other ant or vacant. 
		The next highest growth rate was seen in plants tended by other ants, followed by \textit{Liom.} ants, then vacant plants. 
		The standard deviation of the growth rates also vary with the size of the tree cholla, decreasing as the size of the plants increase, ranging from $-1.089$ to $1.499$.
		\ali{ }{I’m really unsure about what else I should say about this. }

		We broke down the impacts of ant partner on the growth rate by year and found that the effects of each ant on the growth rates of the cacti don’t always align, as shown in Figure \ref{fig:year-ant}. 
		In 2004, 2005, and 2007, the only ant which has a positive effect on the growth rate of the tree cholla. 
		In 2006, \textit{Crem.} has the most positive effect on the growth rate of cacti, followed by Vacant, Other, and \textit{Liom.}. 
		In 2007, 2008, and 2016, vacant had the most negative effect on the growth rates of cacti, while in 2012, vacant plants had experienced the most positive effects on their growth rates. 
		In 2010 and 2012, the only ant which has a negative effect on the growth rate of the cacti. 
		From 2013-2019, the effects of all ant partners are quite tightly coupled (all closely positive or closely negative).

		Our analyses of the bayesian hierarchical survival model showed that large cacti have higher survival rates than small, regardless of the ant partner. 
		It also showed that small cacti had significantly different survival rates depending on the ant partner. 
		Small cacti experienced highest survival rates when tended by \textit{Crem.} (near $70\%$) as compared to the lowest survival rates when tended by \textit{Liom.} or other ants (below $60\%$), as shown in Figure \ref{fig:surv}.
		As tree cholla grow, the probabilities of survival increase no matter the partner to nearly $100\%$ with plants tended by \textit{Crem.} and \textit{Liom.} reaching maximum survival first and plants that are vacant reaching last. 
		\textit{Crem.} tended plants have survival rates ranging from $68.379\%$ to $99.998\%$, with the rates increasing with the size of the cacti.  
		\textit{Liom.} tended plants have survival rates ranging from $35.997\%$ to $99.999\%$, with the rates increasing with the size of the cacti. 
		Other tended plants have survival rates ranging from $15.078\%$ to $99.999\%$, with the rates increasing with the size of the cacti. 
		Vacant plants have survival rates ranging from $22.031\%$ to $99.647\%$, with the rates increasing with the size of the cacti.

		We broke down the survival rates by year to determine the differences in ant effects across time. 
		In 2004, 2011, 2014, and 2014, vacant tree cholla experienced more positive effects on their survival rates than any other cacti, while vacant cacti experienced the most negative effects on survival rates in 2005 and 2010.
		In 2007 and 2013, tree cholla tended by \textit{Liom.} experienced significantly more positive effects on the survival rate than any other cacti, whereas in 2018 and 2019 \textit{Liom.} tended cacti experienced the most negative effects on the survival rates. 
		In 2004 and 2009, plants tended by ants in the category of other experienced the most negative effects on survival rates, while in 2017 these plants experienced the most positive effects on the survival rates. 
		\textit{Crem.} tended tree cholla experienced more negative effects on the survival rates than any other cacti. 
		\textit{Crem.}, \textit{Liom.}, and Other-tended plants all experience similar patterns of positive and negative effects on survival rates through most years, with exceptions between the years of 2009-2010, 2011-2012, and 2017-2019.

		Tree cholla tended by \textit{Liom.} ants had significantly higher viability rates, from $79.83\%$ to $91.81\%$ with a mean of $87.047\%$, as compared to those of cacti tended by \textit{Crem.}, from $69.19\%$ to $87.60\%$ with a mean of $79,784\%$, and other, from $76.98\%$ to $86.20\%$ with a mean of $76.977\%$, as shown in Figure \ref{fig:viab}. 
		The lowest observed viability rate of tree cholla flower buds ranged from $62.83\%$ to $83.78\%$ with a mean of $74.604\%$ when there were no ant partners. 
		Using a chi squared test I determined that there is a $13.6\%$ chance that this difference between the mean viability rates of \textit{Liom.} tended plants and vacant plants.

		We broke the effects of ant partners on the viability rates of cacti down by year and found that in some years the effects of different ant partners on the viability rates of the cacti are coupled while in others they differ significantly. 
		IN 2004 vacant cacti experienced the most positive effects on their viability rates, whereas in 2005, vacant cacti experienced the most negative effects on their viability rates compared to other cacti. 
		In 2006 and 2017, \textit{Crem.} tended cacti experienced the most positive effects on viability rates, while in 2012, 2014, 2016, and 2018, \textit{Crem.} tended cacti experienced the most negative effects on viability rates. 
		In 2005,2013, 2015, and 2019, cacti tended by ants in the other category experienced the most positive effects on the viability rates, while in 2006 they experienced the most negative effects. 
		In 2012, \textit{Liom} tended cacti experienced the most positive effects on their viability rates, while in 2019 they experienced the most negative. 
		From the years 2013 to 2019, the effects of all ant partners on the viability rates of cacti are tightly coupled in patterns from positive to negative.

		\subsection*{Ant Transition Rates}
		All very small cacti are vacant with the probability of an ant partner increasing as the cacti grow larger, as shown in Figure \ref{fig:ant}. 
		Most large tree cholla are tended by \textit{Liom.} ants even if they had a different previous partner.
		The largest vacant cacti have a $42.875\%$ probability of being tended by \textit{Liom.} ants in the next season, $7.143\%$ probability of being tended by other ants in the next season, $28.571\%$ probability of being tended by \textit{Crem.}, and $21.429\%$ probability of being vacant in the next season.
		Previously vacant cacti are most likely to stay vacant until the cacti reach about $10 log(m)^3$, at which point they are more likely to be tended by \textit{Liom.} ants in the next season. 
		Large cacti tended by \textit{Liom.} ants are likely to be tended by \textit{Liom.} ants again ($90.476\%$) in the next season.
		They have a $2.372\%$ probability of being tended by \textit{Crem.} ants in the next season, $7.143\%$ probability of being tended by other ants in the next season, and $asdfasdf$ probability of being vacant.  
		Previously \textit{Liom.} tended cacti are most likely to be vacant until they reach the size of about $7 log(m^3)$, at which point they are most likely to be tended by \textit{Liom.} in the next season.
		Only large tree cholla previously tended by \textit{Crem.} are more likely to be tended by \textit{Crem.} again than be tended by \textit{Liom.} ants in the next year. 
		Large tree cholla tended by \textit{Crem.} have a $47.059\%$ probability of being tended by \textit{Crem.} in the next season, $33.333\%$ probability of being tended by \textit{Liom.} in the next season, $30\%$ probability of being tended by other ants in the next season, and $33.333\%$ probability of being vacant. 
		Previously \textit{Crem.} tended plants are most likely to become vacant in the next season until they reach the size of about $15 log(m^3)$, after which they are more likely to remain tended by \textit{Crem.} ants. 
		Cacti previously tended by other ants have a $24.138\%$ probability of being tended by \textit{Crem.} in the next season, $69.231\%$ probability of being tended by \textit{Liom.} in the next season, $7.692\%$ probability of being tended by other ants in the next season, and $23.076\%$ probability of being vacant. 
		Medium cacti follow the same patterns as large cacti in partner transitions.

		\subsection*{Demographic Modeling}
		We considered both a deterministic Integral Projection Model and a stochastic one to contrast the differences. 
		In the deterministic model, we found that simulations with all ant partners (and vacancy) present resulted in the highest mean population growth rate while populations with no ant partners had the lowest mean population growth rate, as shown in Figure \ref{fig:lambda}.
		The estimated mean population fitness of tree cholla when all ants were present was higher than the mean population fitness of any other scenario.
		Similarly, only a few other scenarios had means within the interquartile range of this high partner diversity scenario. 
		Honestly have no idea how much detail I should go into in this?

		\section*{Discussion}
		\subsection*{Vital Rates}
		\textbf{Ant partners have contrasting effects on vital rate processes of tree cholla.}
		Regression analyses showed that the different ant partners had significantly different impacts on the various vital rate processes of the tree cholla cacti. 
		Specifically, \textit{Crem.} tended cacti have advantages, at small sizes, over cacti tended by any other ant or vacant. 
		\textit{Crem.} tended tree cholla had the highest survival rates (Figure \ref{fig:surv})  at small sizes and the highest growth rates (Figure \ref{fig:grow}), two of the most important vital rates for small cacti which are not yet reproducing. 
		On the other hand, reproducing cacti which have \textit{Liom.} partners  have advantages with the highest viability rates of flower buds (Figure \ref{fig:viab}). 
		Together this indicates that the best partner may change as the cacti grow and begin to reproduce, when the most vulnerable part of the plant is the flower with the seeds. 
		This reflects the changes in the resource use of tree cholla as they begin to use their resources for reproduction rather than growth. 
		The fact that different ant partners have significantly different effects on the various vital rates of tree cholla indicates that none of them are the “perfect” partner, and that the “best” partner may in fact change over the lifespan of the cacti. 
		As the tree cholla grew, the best partner changed from \textit{Crem.} ants, partners known for ***, to \textit{Liom.} ants, partners best known for defensive benefits to the cacti, particularly against the seed predators which most impact viability. 
		The difference in ant partners made a significant difference in the observed vital rates of the cacti, indicating that considering the interaction between the tree cholla and any individual partner would fail to capture the extent of the benefits to the cacti.
		Like many other systems, pairwise perspectives do not fully encompass the complex impacts that multispecies mutualisms have on the focal mutualists vital rates.

		\subsection*{Ant Transition Rates}
		\textbf{Small cacti remain vacant, while large cacti are most likely to be tended by \textit{Liom.} ants.}
		Small cacti are unlikely to be tended because most do not produce EFN, of if they do it is a very small amount. 
		Medium-sized to large cacti are much more likely to be tended than vacant as they begin producing EFN, with many factors that determine the most likely partner. 
		Some of the ant partners appear to have high turnover rates, meaning they are unlikely to tend the same plant multiple years in a row. 
		Ants in the other category have high turnover rates, shown by the fact that medium and large cacti tended by other are unlikely to be tended by other ants again in the next season. 
		The reason for these turnovers could be due to the inability to defend their territories, an ability to find and colonize new resources, or an ability to colonize resources that have been left unclaimed. 
		This discovery-dominancy tradeoff is a well-studied hypothesis in ant literature \cite{lach2010} that could explain the remaining presence of ants in the other category despite high turnover rates.

		On the other hand, \textit{Crem.} ants appear to have lower turnover rates, since large cacti have up to $47.059\%$ probability of being tended by \textit{Crem.} in the next year.
		In addition to turnover rates, there are also colonization rates, the probability of a species taking over a cactus that was previously tended by different ants. 
		\textit{Liom.} are the only ant partners we observed with high colonization rates. 
		Most cacti tended by non-\textit{Liom.} ants have a high probability of being taken over by \textit{Liom} ants in the next season, as shown in Figure \ref{fig:ant}.
		This pattern could be due to the well-known high levels of aggression displayed by \textit{Liom.} ants in this system, however there are other possible explanations, such as nectar composition.
		The exception to this rule are plants tended by \textit{Crem.} ants which are more likely to remain tended by \textit{Crem.} than be taken over by \textit{Liom.} in the next season. 
		The trend that most large ants are likely to be tended by \textit{Liom.} ants reflects the findings that large cacti benefit most from \textit{Liom.} as ant partners. 
		As explained in the introduction, there are many factors that determine the colonization rates of different cacti by their ant partners, including EFN quantity and quality, ability to seek out cacti, aggression, and more.
		These patterns could be explained by the \textit{Liom.} ants ability to dominate at a resource site and therefore takeover from different ants which originally found the site.
